Differential geometric algebra with Leibniz and Grassmann

### 2019-10-27 paper/paper.tex
improved Betti numbers, paper revisions, changed Blade to Simplex

\maketitle
\begin{figure}[ht]
\centerline{\includegraphics[width=4cm]{grassmann.png}}
\caption*{github.com/chakravala/Grassmann.jl}
\end{figure}
\begin{itemize}
	\item \textbf{DirectSum.jl}: Abstract tangent bundle vector space types (unions, intersections, sums, etc.)
	\item \textbf{AbstractTensors.jl}: Tensor algebra abstract type interoperability with vector bundle parameter	
	\item \textbf{Grassmann.jl}: $\langle$Leibniz+Grassmann-Clifford-Hestenes$\rangle$ differential geometric algebra of multivector forms
	\item \textbf{Leibniz.jl}: Derivation operator algebras for tensor fields
	\item \textbf{Reduce.jl}: Symbolic parser generator for Julia expressions using REDUCE algebra term rewriter
\end{itemize}
\begin{abstract}
	The \textit{Grassmann.jl}
	package provides tools for computations based on multi-linear algebra and spin groups using the extended geometric algebra known as Leibniz-Grassmann-Clifford-Hestenes algebra.
	Combinatorial products include
	exterior, regressive, inner, and geometric; along with the Hodge star, adjoint, reversal, and boundary operators.
	The kernelized operations are built up from composite sparse tensor products and Hodge duality, with high dimensional support for up to 62 indices using staged caching and precompilation. Code generation enables concise with highly extensible definitions.
	\textit{DirectSum.jl}
	multivector parametric type polymorphism is based on tangent vector spaces and conformal projective geometry.
	Additionally, the universal interoperability between different sub-algebras is enabled by \textit{AbstractTensors.jl},
	on which the type system is built.
	%\headingtable
\end{abstract}
Mathematical foundations and some of the nuances in the definitions specific to the \textit{Grassmann.jl} implementation are concisely described, along with the accompanying support packages that provide an extensible platform for computing with geometric algebra at high dimensions.
The design is based on the \verb`TensorAlgebra` abstract type interoperability from \textit{AbstractTensors.jl} with a \verb`VectorBundle` type parameter from \textit{DirectSum.jl}. Abstract vector space type operations happen at compile-time, resulting in a differential conformal geometric algebra of hyper-dual multivector forms.

@@

It is possible to reach \verb`Basis` elements with up to $n=62$ indices, % with \verb`TensorAlgebra` having higher maximum dimensions than supported by Julia natively.
requiring full alpha-numeric labeling with lower-case and capital letters. 
Full \verb`MultiVector` allocations are only possible for $n\leq22$, but sparse operations are also available at higher dimensions.
While \verb`Grassmann.Algebra{V}` is a container for the \verb`TensorAlgebra` generators of $V$, the \verb`Grassmann.Algebra` is only cached for $n\leq8$.
For the range of dimensions $8<n\leq22$, the \verb`Grassmann.SparseAlgebra` type is used.
To reach higher dimensions with $n>22$, the \verb`Grassmann.ExtendedAlgebra` type is used.

@@

\begin{definition}
	[Null-basis of projective split]
	Let $v_\pm^2 = \pm1$ be a basis with $v_\infty = v_++v_-$ and $v_\emptyset = (v_--v_+)/2$
\end{definition}
An embedding space $\mb R^{n+1,1}$ carrying the action from the group $SO(n+1,1)$ then has
$v_\infty^2 =0$, $v_\emptyset^2 =0$,
$v_\infty \cdot v_\emptyset = 1$,  and $v_{\infty\emptyset}^2 = 1$ with
Minkowski plane $v_{\infty\emptyset}$ having the Hestenes-Dirac-Clifford product properties
\begin{align*}
	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, \\
	v_\infty\ominus v_\emptyset &= -1 + v_{\infty\emptyset}, & v_\emptyset\ominus v_\infty &=  -1 - v_{\infty\emptyset}
\end{align*}

\begin{definition}
	Symmetry properties of the tensor algebra can be characterized in terms of the geometric product by two averaging operations, which are the symmetrization $\odot$ and anti-symmetrization $\boxtimes$ operators:
	\begin{align*}
		\bigodot_{k=1}^j \omega_k &= \frac1{j!}\sum_{\sigma\in S_P}\bigominus_k\omega_{\sigma(k)}, &
		\bigboxtimes_{k=1}^j \omega_k &= \sum_{\sigma\in S_P}\frac{(-1)^{\Pi(\sigma)}}{j!}\bigominus_k\omega_{\sigma(k)}
	\end{align*}
\end{definition}
These products satisfy various \verb`MultiVector` properties, including the associative and distributive laws.

@@

\begin{definition}[Reverse, involute, conjugate]
	The \verb`reverse` of $\gen{\omega}_r$ is defined as $\gen{\tilde\omega}_r = (-1)^{(r-1)r/2}\gen{\omega}_r$, while the \verb`involute` is $(-1)^r\gen{\omega}_r$ and Clifford \verb`conj`  $\gen{\omega}_r^\ddagger$ is the composition of \verb`involute` and \verb`reverse`.
\end{definition}

\begin{definition}[Reversed product]
	Define the index reversed product $\ast$ which yields a Hilbert space structure:
	\begin{align*}
		\omega\ast\eta &= \tilde\omega\ominus\eta, & \text{or} & & \omega\ast'\eta &= \omega\ominus\tilde\eta,
	\end{align*}
	\begin{align*}
		|\omega|^2 &= \omega\ast\omega, & |\omega| &= \sqrt{\omega\ast\omega}, & ||\omega|| = \text{Euclidean }|\omega|.
	\end{align*}
\end{definition}
\begin{definition}[Sandwich product]
	This product can be defined as $\eta\oslash\omega = (\eta\ast\omega)\ominus\eta$. Alternatively, the reversed definition is $\eta\obackslash\omega = \eta\ominus(\omega\ast'\eta)$ or in Julia $\eta\,$\verb`>>>`$\,\omega$, which is often found in literature.
\end{definition}
\begin{remark}
	Observe that $\ast$ and $\ast'$ could both be exchanged in \verb`abs`, \verb`abs2`, and \verb`norm`; however, these are different products.
	The \textit{scalar product} $\circledast$ is the scalar part of the reversed product $\eta\circledast\omega = \gen{\eta\ast\omega}$.
	In general $\sqrt\omega = e^{(\log\omega)/2}$ is valid for \verb`inv`ertible multivectors $\omega\inv = \omega\ast|\omega|^{-2} = \tilde\omega/|\omega|^2$, where $\eta/\omega = \eta\ominus\omega\inv = \eta\ominus(\tilde\omega/(\omega\oslash1))$.
	Observe that it is overall more simple and consistent to use the $\ast$ and $\oslash$ operations instead of the $\ast'$ and $\obackslash$ variations.
\end{remark}
The \verb`real` part $\Re\omega = (\omega+\tilde\omega)/2$ is defined by $|\Re\omega|^2 = (\Re\omega)^{\ominus2}$ and the \verb`imag` part $\Im\omega = (\omega-\tilde\omega)/2$ by $|\Im\omega|^2 = -(\Im\omega)^{\ominus2}$, such that for any multivector $\omega = \Re\omega+\Im\omega$ has real and imaginary partitioned by
\begin{align*}
	\gen{\tilde\omega}_r/\mlr{\gen{\omega}_r} &= \sqrt{\gen{\tilde\omega}_r^2/\big|\gen{\omega}_r\big|^2} = \sqrt{\gen{\omega}_r\ast\gen{\omega}_r\inv} \\
	&= \sqrt{\gen{\tilde\omega}_r/\gen{\omega}_r}=\sqrt{(-1)^{(r-1)r/2}} \in\set{1,\sqrt{-1}},
\end{align*}
which is a unique partitioning completely independent of the metric space and manifold of the algebra \cite{chappell-iqbal-gunn-abbott}.
$$ \omega\ast\omega = |\omega|^2 = |\Re\omega+\Im\omega|^2 = %|\Re\omega|^2 + |\Im\omega|^2 + \Re\omega\ast\Im\omega + \Im\omega\ast\Re\omega =
|\Re\omega|^2+|\Im\omega|^2 + 2\Re(\Re\omega\ast\Im\omega) $$
The \verb`radial` and \verb`angular` components in a multivector exponential are partitioned by the parity of their metric.

@@

\begin{definition}[Poincare-Hodge dual complement]
	Let $\star\gen{\omega}_p = \gen{\omega}_p\ast I = \gen{\tilde\omega}_p\ominus I$, %= (-1)^{\frac{p(p+1)}2+\us k\sum i_k}\det\mat{ g_{i_ki_k}}\bigwedge_{m\in J(\omega)} w_m
	 then $\star : \Lambda^pV\ra\Lambda^{n-p}V$.
\end{definition}
\begin{remark}
	While $\star\omega$ is \verb`complementright` of $\omega$, the \verb`complementleft` would be $I\ast'\omega$. The $\star$ symbol was added to the Julia language as unary operator for ease of use with \verb`Grassmann` on Julia's v1.2 release.
\end{remark}
\begin{lstlisting}[language = Julia]
using Grassmann, Compose
x = Grassmann.Algebra(ℝ^7).v123
Grassmann.graph(⋆(x)+x)
draw(PDF("simplex.pdf",16cm,16cm),⋆(x)+x)
\end{lstlisting}
\begin{figure}[ht]
\centerline{\includegraphics[width=0.42\textwidth]{triangle-tetrahedron.png}}
\caption*{Triangle with its tetrahedron complement $\star v_{123} + v_{123}$ in $\mb R^7$}
\end{figure}
John Browne has discussed Grassmann duality principle in book \cite{browne}, stating that every theorem (involving either of the exterior and regressive products) can be translated into its dual theorem by replacing the $\wedge$ and $\vee$ operations and applying \textit{Poincare duality} (homology).
First applying this Grassmann duality principle to the $\wedge$ product alone, let $\set{\omega_k}_k\in\Lambda^{p_k}V, P=\sum_kp_k$, then it is possible to obtain the co-product
$\bigvee :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{P-(g-1)\#V}\bigcup_k V_k$.
Grassmann's original notation implicitly combined $\wedge,\vee,\star$.
The join $\wedge$ product is analogous to union $\cup$, the meet $\vee$ product is analogous to intersection $\cap$, and the orthogonal complement $\star\mapsto^\perp$ is negation.
Together, $(\wedge,\vee,\star)$ yield an orthocomplementary propositional lattice (quantum logic):
\begin{align*}
	(\star\bigvee_k &\omega_k)(v_1,\dots,v_P) = (\bigwedge_k\star\omega_k)(v_1,\dots,v_P) \quad \textit{DeMorgan's Law},
\end{align*}
where DeMorgan's law is used to derive tensor contractions.
\begin{definition}
	The left $\lrcorner$ and right $\llcorner$ contraction are symmetrically defined
	$ \gen{\omega}_r\cdot\gen{\eta}_s = \begin{cases} \omega\llcorner\eta=\omega\vee\star\eta & r\geq s \\ \omega\lrcorner\eta=\eta\vee\star\omega & r\leq s \end{cases} $.
	Note for $\omega,\eta$ of equal grade, $\omega\circledast\eta = \omega\odot\eta = \omega\cdot\eta = \omega\llcorner\eta = \omega\lrcorner\eta$ are all symmetric operations.
\end{definition}

@@

	Then  substitute this into $\int_M \omega\wedge(-1)^{mk+m+1}\star\star d\star\eta = (-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}\int_M\omega\wedge d\star\eta$,
	with identity $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and
	$ (-1)^k\int_M\omega\wedge d\star\eta = \int_M d(\omega\wedge\star\eta) - (-1)^{k-1}\omega\wedge d\star\eta = \int_M d\omega\wedge\star\eta$.
	Stokes identity can be proved by relying on a variant of the \textit{common factor theorem} by Browne \cite{browne}.
\end{proof}
\begin{theorem}[Clifford-Dirac-Laplacian]
	The Dirac operator is $ \Delta^\frac12\omega = \mp\omega\ominus\nabla = \pm\nabla\wedge\omega \mp \omega\llcorner\nabla  = \pm d\omega\mp\partial\omega$ \cite{garling}.
	\begin{align*}
		\Delta\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \pm(\pm\omega\ominus\nabla)\ominus\nabla).
	\end{align*}
	Elements $\omega$ are \textit{harmonic} if $\Delta\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, such that $\mc H^p M = \setc{\Delta\omega = 0}{\omega\in \Omega^pM}$.
	Hodge \cite{ivancevic}:
	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\partial\Omega^{p+1}M}$.
	Note: $\nabla\omega\neq\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
\end{theorem}

>>>>

\maketitle
\begin{figure}[ht]
%\centerline{\includegraphics[width=4cm]{grassmann.png}}
\centerline{\includegraphics[width=4cm]{../docs/src/assets/logo.png}}
\caption*{github.com/chakravala/Grassmann.jl}
\end{figure}
\begin{abstract}
	The \textit{Grassmann.jl}
	package provides tools for computations based on multi-linear algebra and spin groups using the extended geometric algebra known as Leibniz-Grassmann-Clifford-Hestenes algebra.
	Combinatorial products include
	exterior, regressive, inner, and geometric; along with the Hodge star, adjoint, reversal, and boundary operators.
	The kernelized operations are built up from composite sparse tensor products and Hodge duality, with high dimensional support for up to 62 indices using staged caching and precompilation. Code generation enables concise with highly extensible definitions.
	\textit{DirectSum.jl}
	multivector parametric type polymorphism is based on tangent vector spaces and conformal projective geometry.
	Additionally, the universal interoperability between different sub-algebras is enabled by \textit{AbstractTensors.jl},
	on which the type system is built.
	%\headingtable
\end{abstract}
\begin{itemize}
	\item \textbf{DirectSum.jl}: Abstract tangent bundle vector space types (unions, intersections, sums, etc.)
	\item \textbf{AbstractTensors.jl}: Tensor algebra abstract type interoperability with vector bundle parameter
	\item \textbf{Grassmann.jl}: $\langle$Leibniz+Grassmann-Clifford-Hestenes$\rangle$ differential geometric algebra of multivector forms
	\item \textbf{Leibniz.jl}: Derivation operator algebras for tensor fields
	\item \textbf{Reduce.jl}: Symbolic parser generator for Julia expressions using REDUCE algebra term rewriter
\end{itemize}
Mathematical foundations and some of the nuances in the definitions specific to the \textit{Grassmann.jl} implementation are concisely described, along with the accompanying support packages that provide an extensible platform for computing with geometric algebra at high dimensions.
The design is based on the \verb`TensorAlgebra` abstract type interoperability from \textit{AbstractTensors.jl} with a \verb`VectorBundle` type parameter from \textit{DirectSum.jl}. Abstract vector space type operations happen at compile-time, resulting in a differential conformal geometric algebra of hyper-dual multivector forms.

@@

It is possible to reach \verb`Simplex` elements with up to $n=62$ vertices, % with \verb`TensorAlgebra` having higher maximum dimensions than supported by Julia natively.
requiring full alpha-numeric labeling with lower-case and capital letters. 
Full \verb`MultiVector` allocations are only possible for $n\leq22$, but sparse operations are also available at higher dimensions.
While \verb`Grassmann.Algebra{V}` is a container for the \verb`TensorAlgebra` generators of $V$, the \verb`Grassmann.Algebra` is only cached for $n\leq8$.
For the range of dimensions $8<n\leq22$, the \verb`Grassmann.SparseAlgebra` type is used.
To reach higher dimensions with $n>22$, the \verb`Grassmann.ExtendedAlgebra` type is used.

@@

\begin{definition}
	[Null-basis of projective split]
	Let $v_\pm^2 = \pm1$ be a basis with $v_\infty = v_++v_-$ and $v_\emptyset = (v_--v_+)/2$
An embedding space $\mb R^{p+1,q+1}$ carrying the action from the group $O(p+1,q+1)$ then has
$v_\infty^2 =0$, $v_\emptyset^2 =0$,
$v_\infty \cdot v_\emptyset = 1$,  and $v_{\infty\emptyset}^2 = 1$ with
Minkowski plane $v_{\infty\emptyset}$ having the Hestenes-Dirac-Clifford product properties
\begin{align*}
	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, \\
	v_\infty\ominus v_\emptyset &= -1 + v_{\infty\emptyset}, & v_\emptyset\ominus v_\infty &=  -1 - v_{\infty\emptyset}
\end{align*}
\end{definition}
\begin{definition}
	Symmetry properties of the tensor algebra can be characterized in terms of the geometric product by two averaging operations, which are the symmetrization $\odot$ and anti-symmetrization $\boxtimes$ operators:
	\begin{align*}
		\bigodot_{k=1}^j \omega_k &= \frac1{j!}\sum_{\sigma\in S_P}\bigominus_k\omega_{\sigma(k)}, &
		\bigboxtimes_{k=1}^j \omega_k &= \sum_{\sigma\in S_P}\frac{(-1)^{\Pi(\sigma)}}{j!}\bigominus_k\omega_{\sigma(k)}
	\end{align*}
\end{definition}
These products satisfy various \verb`MultiVector` properties, including the associative and distributive laws.

@@

\begin{definition}[Reverse, involute, conjugate]
	The \verb`reverse` of $\gen{\omega}_r$ is defined as $\gen{\tilde\omega}_r = (-1)^{(r-1)r/2}\gen{\omega}_r$, while the \verb`involute` is $\gen{\omega}_r^\times=(-1)^r\gen{\omega}_r$ and Clifford \verb`conj`  $\gen{\omega}_r^\ddagger$ is the composition of \verb`involute` and \verb`reverse`.
\end{definition}

\begin{definition}[Reversed product]
	Define the index reversed product $\ast$ which yields a Hilbert space structure:
	\begin{align*}
		\omega\ast\eta &= \tilde\omega\ominus\eta, & \text{or} & & \omega\ast'\eta &= \omega\ominus\tilde\eta,
	\end{align*}
	\begin{align*}
		|\omega|^2 &= \omega\ast\omega, & |\omega| &= \sqrt{\omega\ast\omega}, & ||\omega|| = \text{Euclidean }|\omega|.
	\end{align*}
\end{definition}
\begin{remark}
	Observe that $\ast$ and $\ast'$ could both be exchanged in \verb`abs`, \verb`abs2`, and \verb`norm`; however, these are different products.
	The \textit{scalar product} $\circledast$ is the scalar part, so $\eta\circledast\omega = \gen{\eta\ast\omega}$.
	In general $\sqrt\omega = e^{(\log\omega)/2}$ is valid for invertible $\omega$.
\end{remark}
\begin{definition}[Inverse]
	$\omega\inv = \omega\ast(\omega\ast\omega)\inv = \tilde\omega/|\omega|^2$, with $\eta/\omega = \eta\ominus\omega\inv$ and % = \eta\ominus(\tilde\omega/(1\oslash\omega))$.
	$\eta\bs\omega = \eta\inv\ominus\omega$.
\end{definition}
\begin{definition}[Sandwich product]
	This product can be defined as $\eta\oslash\omega = \omega\bs\eta\ominus\omega^\times$. Alternatively, the reversed definition is $\eta\obackslash\omega = \eta^\times\ominus\omega/\eta$ or in Julia $\eta\,$\verb`>>>`$\,\omega$, which is often found in literature.
\end{definition}
\begin{remark}
	Observe that it is overall more simple and consistent to use $\set{\ast,\oslash}$ operations instead of $\set{\ast',\obackslash}$.
\end{remark}
The \verb`real` part $\Re\omega = (\omega+\tilde\omega)/2$ is defined by $|\Re\omega|^2 = (\Re\omega)^{\ominus2}$ and the \verb`imag` part $\Im\omega = (\omega-\tilde\omega)/2$ by $|\Im\omega|^2 = -(\Im\omega)^{\ominus2}$, such that $\omega = \Re\omega+\Im\omega$ has real and imaginary partitioned by
\begin{align*}
	\gen{\tilde\omega}_r/\mlr{\gen{\omega}_r} &= \sqrt{\gen{\tilde\omega}_r^2/\big|\gen{\omega}_r\big|^2} = \sqrt{\gen{\omega}_r\ast\gen{\omega}_r\inv} \\
	&= \sqrt{\gen{\tilde\omega}_r/\gen{\omega}_r}=\sqrt{(-1)^{(r-1)r/2}} \in\set{1,\sqrt{-1}},
\end{align*}
which is a unique partitioning completely independent of the metric space and manifold of the algebra \cite{chappell-iqbal-gunn-abbott}.
$$ \omega\ast\omega = |\omega|^2 = |\Re\omega+\Im\omega|^2 = %|\Re\omega|^2 + |\Im\omega|^2 + \Re\omega\ast\Im\omega + \Im\omega\ast\Re\omega =
|\Re\omega|^2+|\Im\omega|^2 + 2\Re(\Re\omega\ast\Im\omega) $$
The \verb`radial` and \verb`angular` components in a multivector exponential are partitioned by the parity of their metric.

@@

\begin{definition}[Poincare-Hodge dual complement]
	Let $\star\gen{\omega}_p = \gen{\omega}_p\ast I = \gen{\tilde\omega}_p\ominus I$, %= (-1)^{\frac{p(p+1)}2+\us k\sum i_k}\det\mat{ g_{i_ki_k}}\bigwedge_{m\in J(\omega)} w_m
	 then $\star : \Lambda^pV\ra\Lambda^{n-p}V$.
\end{definition}
\begin{remark}
	While $\star\omega$ is \verb`complementright` of $\omega$, the \verb`complementleft` would be $I\ast'\omega$. The $\star$ symbol was added to the Julia language as unary operator for ease of use with \verb`Grassmann` on Julia's v1.2 release.
\end{remark}
\begin{lstlisting}[language = Julia]
using Grassmann, Compose
x = Grassmann.Algebra(ℝ^7).v123
Grassmann.graph(x+!x)
draw(PDF("simplex.pdf",16cm,16cm),x+!x)
\end{lstlisting}
\begin{figure}[ht]
\centerline{\includegraphics[width=0.42\textwidth]{triangle-tetrahedron.png}}
\caption*{Triangle with its tetrahedron complement $v_{123} + \star v_{123}$ in $\mb R^7$}
\end{figure}
John Browne has discussed Grassmann duality principle in book \cite{browne}, stating that every theorem (involving either of the exterior and regressive products) can be translated into its dual theorem by replacing the $\wedge$ and $\vee$ operations and applying \textit{Poincare duality} (homology).
First applying this Grassmann duality principle to the $\wedge$ product alone, let $\set{\omega_k}_k\in\Lambda^{p_k}V, P=\sum_kp_k$, then it is possible to obtain the co-product
$\bigvee :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{P-(g-1)\#V}\bigcup_k V_k$.
Grassmann's original notation implicitly combined $\wedge,\vee,\star$.
The join $\wedge$ product is analogous to union $\cup$, the meet $\vee$ product is analogous to intersection $\cap$, and the orthogonal complement $\star\mapsto^\perp$ is negation.
Together, $(\wedge,\vee,\star)$ yield an orthocomplementary propositional lattice (quantum logic):
\begin{align*}
	(\star\bigvee_k &\omega_k)(v_1,\dots,v_P) = (\bigwedge_k\star\omega_k)(v_1,\dots,v_P) \quad \textit{DeMorgan's Law},
\end{align*}
where DeMorgan's law is used to derive tensor contractions.
\begin{definition}
	Skew left $\lrcorner$ and right $\llcorner$ contractions are symmetrically defined
	$ \gen{\omega}_r\cdot\gen{\eta}_s = \begin{cases} \omega\llcorner\eta=\omega\vee\star\eta & r\geq s \\ \omega\lrcorner\eta=\eta\vee\star\omega & r\leq s \end{cases} $.
	Note for $\omega,\eta$ of equal grade, $\omega\circledast\eta = \omega\odot\eta = \omega\cdot\eta = \omega\llcorner\eta = \omega\lrcorner\eta$ are all symmetric operations. In Julia, $\lrcorner$ is $<$ and $\llcorner$ is $>$.
\end{definition}

@@

	Then  substitute this into $\int_M \omega\wedge(-1)^{mk+m+1}\star\star d\star\eta = (-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}\int_M\omega\wedge d\star\eta$,
	with identity $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and
	$ (-1)^k\int_M\omega\wedge d\star\eta = \int_M d(\omega\wedge\star\eta) - (-1)^{k-1}\omega\wedge d\star\eta = \int_M d\omega\wedge\star\eta$.
	Stokes identity can be proved by relying on a variant of the \textit{common factor theorem} by Browne \cite{browne}.
\end{proof}
\begin{theorem}[Clifford-Dirac-Laplacian]
	The Dirac operator \cite{garling} is $ \Delta^\frac12\omega = \pm\nabla\ominus\omega = \pm\nabla\wedge\omega \pm \nabla\cdot\omega  = \pm d\omega\pm\partial\omega$.
	\begin{align*}
		\Delta\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \pm(\pm\omega\ominus\nabla)\ominus\nabla).
	\end{align*}
	Elements $\omega$ are \textit{harmonic} if $\Delta\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, such that $\mc H^p M = \setc{\Delta\omega = 0}{\omega\in \Omega^pM}$.
	Hodge \cite{ivancevic}:
	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\partial\Omega^{p+1}M}$.
	Note: $\nabla\omega=-\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
\end{theorem}
